### 2025-04-24 thesis/thesis.tex
Fix error

In this section a comprehensive literature review is performed to asses the research landscape on NL2SQL
(sometimes also referred to as Text-to-SQL or T2SQL) and NLIDBs. Following their development starting in
the late 1990s and early 2000s \citep{NLIDBs, NLIDBTheory, ILPParsing, ILPParsing2} until now, observing multiple 
larger paradigm shifts happening over time \citep{GRAPPA, STRUG, Seq2SQL, NALIR, SQLizer}. In particular this 
research focuses on the recent advancements when it comes to language models and how they can be harnessed for
effective NL2SQL systems \citep{LLM-Sql, T2SQL-LLM-Bench, T2SQL-LLM-Bench-2, T2SQL-LLM-Bench-3, SPIDER2, BIRD}.

>>>>

In this section a comprehensive literature review is performed to asses the research landscape on NL2SQL
(sometimes also referred to as Text-to-SQL or T2SQL) and NLIDBs. From the time their development accelerated in
the late 1990s and early 2000s \citep{NLIDBs, NLIDBTheory, ILPParsing, ILPParsing2} until now, observing multiple 
larger paradigm shifts happening over time \citep{GRAPPA, STRUG, Seq2SQL, NALIR, SQLizer}. In particular this 
research focuses on the recent advancements when it comes to language models and how they can be harnessed for
effective NL2SQL systems \citep{LLM-Sql, T2SQL-LLM-Bench, T2SQL-LLM-Bench-2, T2SQL-LLM-Bench-3, SPIDER2, BIRD}.
